Data

### 2019-10-04 analysis/data.Rmd
wflow_publish(c("analysis/data.Rmd", "analysis/setup.Rmd", "analysis/paper.Rmd", "analysis/website.Rmd"))

```{bash ,eval=FALSE}
# enable relevant Python virtual environment (Python 2) if you have one, and you should.
$ pyenv activate anaconda2-4.2.0
$ cd data-raw
$ gsutil cp \
    gs://pru-trajectories/products/synth_positions/cpr_fr24/mas_05_cpr_fr24_synth_positions_2017-08-03.csv.bz2 .
```

As explained in the paper, you can use `R/extract-arrivals.R` to produce CSV files
containing only the flights and positions for your airport of initerest.
You should edit the relevant configuration values at the beginning of the script before launching it.
You will get:

@@

* Position reports for arrival at `<airport>` on `<date>`
  are in a CSV file `<airport>_pos_rt_<date>.csv`.
  For example `eidw_pos_rt_2017-08-01.csv` is for arrivals to
  Dublin Airport (ICAO's id EIDW) on Aug, 1 2017.

>>>>

```{bash ,eval=FALSE}
# enable relevant Python virtual environment (Python 2) if you have one, and you should.
$ pyenv activate anaconda2-4.2.0
$ cd data-raw
$ gsutil cp \
    gs://pru-trajectories/products/synth_positions/cpr_fr24/mas_05_cpr_fr24_synth_positions_2017-08-03.csv.bz2 .
$ gsutil cp \
    gs://pru-trajectories/sources/merged/overnight_cpr_fr24/cpr_fr24_flights_2017-08-03.csv.bz2 .
```

As explained in the paper, you can use `R/extract-arrivals.R` to produce CSV files
containing only the flights and positions for the airports of initerest.
You should edit the relevant configuration values at the beginning of the script before launching it.
You will get:

@@

* Position reports for arrival at `<airport>` on `<date>`
  are in a CSV file `<airport>_pos_rt_<date>_raw.csv` (and `<airport>_pos_rt_<date>.csv`
  for smoothed trajectories, i.e. median filter for longitude,latitude amd altitude.)
  For example `eidw_pos_rt_2017-08-01.csv` is for (smoothed trajectories) arrivals to
  Dublin Airport (ICAO's id EIDW) on Aug, 1 2017.
